---
title: "R Study Note"
output: html_notebook
---
Ruidi Zhao's R study note. 

```{r}
x <- c(1,2,3,4)
y <- c(3,4,5,6)
```

`ls()` is used to look at a list of all of the objects <br>
`rm()` is used to delete any that we don't wat
```{r}
ls() 
rm(x, y) 
ls()
```
```{r}
rm(list=ls()) # remove everything at once
```

## Matrix
```{r}
x = matrix(data = c(1,2,3,4), nrow = 2, ncol = 2)
x
```

`byrow`的话就是按照row的方向排element
```{r}
matrix(c(1,2,3,4), 2, 2, byrow = TRUE)
```

## Random Variables
```{r}
# set.seed(0)
# So that you can reproduce the result

x = rnorm(50,mean = 0, sd = 1)
y = x + rnorm(50, mean = 50, sd = 0.1)
cor(x, y) # Get the correlation between x and y 
var(x)
sd(x)
```

## Graphics
The `plot()` function is the primary way to plot data in R. 
```{r}
x = rnorm(100)
y = rnorm(100)
plot(x, y, xlab = 'x-axis', ylab = 'y-axis', main = 'Plot of X vs Y')
```

save the graph
```{r}
pdf('Figure.pdf') # save it as pdf
# jpeg('Figure.jpeg') # save it as jpeg
plot(x, y, col = 'green')
dev.off() # Tell R that we are done creating the plot
```
Create contour plot with `contour()`, it takes three arguments:
1. A vector of the x values (the first dimension)
2. A vector of the y values (the second dimension), and 
3. A matrix whose elements correspond to the z value (the third dimension) for each pair of (x, y) corrdinates

```{r}
x = seq(1, 10) # or x = 1:10
y = x
f = outer(x, y, function(x, y)cos(y)/(1 + x^2))
contour(x, y, f)
```
Heatmap 
```{r}
image(x, y, f)
```
Use `persp()`
```{r}
persp(x, y, f, theta = 30, phi = 20)
# Theta and phi control the angles at which the plot is viewed
```
## Indexing Data
```{r}
A = matrix(1:16, 4, 4)
A
A[2,3]
```
```{r}
A[c(1, 3), c(2, 4)] # Select multiple row and column
A[1:3, 2:4]
A[, 1:2]
A[1:2, ]
A[-2, ] # '-' means except
dim(A) # The dimension of A, 就是python里的shape?
```
## Loading Data



